Transitivity of Subtyping for Intersection Types

### 2019-06-21 papers/intersection-transitivity.tex
check

\begin{definition}[factor]

\end{definition}

\begin{lemma}
  If
\begin{itemize}
\item $\neg\, \mathsf{topCod}(D)$,
\item $D ⊆ C$, and
\item for any $A,B$, if $\neg\,\mathsf{top}(B)$ and $A → B ∈ D$,
     then $A → B$ factors $u_2$ into some type $u_3$,
\end{itemize}
then $\dom{D} → \cod{D}$ factors $u_2$ into some type $u_4$.
\end{lemma}

>>>>

\begin{definition}[factors]
  We say $A → B$ \emph{factors} $C$
  if there exists some type $C'$ such that
  $C' ⊆ C$, $\neg\,\mathsf{topCod}(C')$, $A <: \dom{C'}$, and $\cod{C'} <: B$.
\end{definition}

\begin{lemma}
  If $\neg\,\mathsf{top}(w)$
  and $u_1$
\end{lemma}

\begin{lemma}
  If
  \begin{itemize}
  \item $\neg\, \mathsf{topCod}(D)$,
  \item for any $A,B$, if $\neg\,\mathsf{top}(B)$ and $A → B ∈ D$,
    then $A → B$ factors $C$,
  \end{itemize}
  then $\dom{D} → \cod{D}$ factors $C$.
\end{lemma}
